master thesis

### 2018-03-24 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Biological view: refine text

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Biological view} \label{sec:biological view}
      To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
        selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
        Apicomplexa. \\
      In Table \ref{table:phylum leaf nodes states} we compare the given states with the predicted ones. \\
      There are several factors that play a role here, and in part, crystallize in these examples. \\
      An important factor here is that the credibility of the results with the accuracy of the input 
        data, i. the data of GloBI, stands and falls. Errors of incorrect input data can be amplified by 
        incorrect prediction of unknown species and can be reversed in order to improve the data 
        situation of GloBI. \\
      Since we look at such large trees we can not expect to know all the parasites, so we look at 
        individual positives. Positive in the sense that the majority have the opposite state.

      \begin{table}[h]
        \begin{center}
          \begin{tabular}{ |l|r||r|r||r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{4}{c|}{\bfseries final states} \\
            \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P & \bfseries 0 \bfseries (FL) & \bfseries 0.3 &\bfseries  0.5 & \bfseries 1 (P) \\
            \hline \hline
            Chordata & 91785        & 10451 & 18          & 91759 & 0 & 0 & 26 \\
            &                       & 99.83~\% & 0.49~\%  & 99.97~\% & & & 0.03~\% \\ \hline
            Nematoda & 30127        & 21 & 3289           & 1604 & 142 & 1196 & 27185 \\
            &                       & 0.63~\% & 99.37~\%  & 5.32~\% & 0.47~\% & 3.97~\% & 90.23~\% \\ \hline
            Platyhelminthes & 22683 & 7 & 7086            & 175 & & & 22508 \\
            &                       & 0.1~\% & 99.9~\%    & 0.77~\% & 0 & 0 & 99.23~\% \\ \hline
            Apicomplexa & 1863      & 1 & 255             & 1 & 0 & 0 & 1862 \\
            &                       & 0.39~\% & 99.61~\%  & 0.05~\% & & & 99.95~\% \\
            % \hline \hline
            % Phylum & \# nodes & FL & P
            %   & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            % Arthropoda & 1198981 & 18912 & 11141 
            %   & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
            % & & 62.93~\% & 37.07~\%
            %   & 91.7~\% & 0.11~\% & 1.87~\% & 0.35~\% & 0.14~\% & 5.86~\% \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Phylum (leaf nodes)}
        \label{table:phylum leaf nodes states} 
      \end{table}

      In contrast to the other phyla examined, the phylogeny is more pronounced (less multifurcation) (see 
        Table \ref{table:percentage loss information subtrees}). This results in a weaker spread of errors. 
        This is reflected in the results from the table \ref{table:phylum leaf nodes states}. There are 18 
        parasites as input data and only 8 more are predicted. The chordata mostly consist of free-living 
        species, so this seems believable. We started with 99.83~\%  species and predict 99.97~\% species 
        as free-living (including already known nodes). \todo{A few punctual tests give us the following:}

      \begin{figure}[h!]
        \centering
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
        \caption{Parasites of Phylum: Chordata \\ 
          Input parasites (green) $\rightarrow$ predicted parasites (white $\rightarrow$ green)}
        \label{fig:ChordataParasites}
      \end{figure}

      We mapped the few parasitic spezies in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
      Known parasitic birds belong to the order Sauria. Here we know from Rothschild  here there are 
        breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
        got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
        \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
        known as broodparasite and some others. \\
      An example of the amplification of mistakes here are the carp. There seems to be a paper from the 
        GloBI concluding: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
        (\textit{Cyprinus carpio})\footnote{
          \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
          {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio}
        }. Since there is hardly any information about free-living, it follows that all siblings are 
        also predicted to be parasitic. \\
        % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
        % Snake: Storeria dekayi (probably caused by wrong input data.)
      % \begin{itemize}
      %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
      %   \item Order Anura (1): a toad (Family Bufonidae) - there exists some parasitic species in here, 
      %     they eat fin or pieces of larger fish.
      %   \item Order Siluriformes (1): a catfish (Family Loricariidae) - there exists some parasitic 
      %     species in here.
      % \end{itemize}

@@

      Most species of Platyhelminthes (flatworms) are parasites, although there are also free-living, 
        predatory feeding species. These are summarized in the Turbellaria, while the parasites are 
        divided into three other classes \cite{Ax1961}. This also corresponds to our observations. There 
        is one class (Rhabditophora) that contains all but one single exception of free-living species 
        of this phylum, which includes the Turbellaria. \\
      It should be noted, however, that this classification is outdated, as it has been proven that 
        the Turbellaria are not monophyletic. But we will not go into that here. \\
      For the Platyhelminthes we had more state information for the leaf nodes compared to the other 
        considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
        0.1~\% free-livings and predicted 0.77~\% as free-living spezies. \\

      With the Nematoda it looks more complicated. Large parts of Nematoda are free-living, but we 
        found only 5.32~\% of them. Blaxter et al. estimates the order of 25,000 parasites in the 
        Nematoda \cite{Blaxter2015} and speaks of at least seven independently arosed parasitism 
        \cite{Blaxter1998}. In a recent article Blaxter identifies 18 origins \cite{Blaxter2015} in 
        Nematoda. \\
      The problem at this point, however, is obvious: Hallan speaks of the fact that only 23,00 species 
        were described by the Nematoda but one assumes 1 million or more\footnote{J. Hallan, unpublished; 
          \hyperlink{https://insects.tamu.edu/research/collection/hallan/}
          {https://insects.tamu.edu/research/collection/hallan/}
        }. \todo{Link ist nicht erreichbar!} The parasites have been much more studied and thus we start 
        with only 0.63~\% free-living species. Against such a shifted data situation, the algorithm is 
        almost powerless. And yet the percentage has increased. \\

@@

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{6}{c|}{\bfseries final states} \\
            \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P
              & \bfseries 0 (FL) & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
            \hline \hline
            Chordata & 122546 & 10451 & 18 
              & 122473 & 0 & 0 & 0 & 0 & 73 \\
            Nematoda & 33564 & 21 & 3289 
              & 846 & 0 & 1133 & 0 & 0 & 31585 \\
            Platyhelminthes & 27142 & 7 & 7086 
              & 1010 & 0 & 175 & 0 & 0 & 25957 \\
            Apicomplexa & 2102 & 1 & 255 
              & 1 & 0 & 0 & 0 & 0 & 2101 \\
            % \hline
            % Arthropoda & 1319460 & 18912 & 11141 
            %   & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
            \hline
          \end{tabular}
        \end{center}
        \caption{Phylum (inkl internal nodes)}
        \label{table:Phylum internal nodes}
      \end{table}

      \begin{table}[h!]
        \begin{center}
          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
            \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
              & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
            \hline \hline
            none & 75446 & 45 & 529 
              & 13426 & 220 & 24082 & 0 & 7792 & 5302 & 0 & 24493 \\
            Fungi & 31457 & 577 & 2983
              & 38520 & 0 & 0 & 0 & 5723 & 0 & 0 & 266463 \\
            Chloroplastida & 416478 & 3519 & 77
              & 410795 & 0 & 0 & 0 & 4182 & 0 & 0 & 1501 \\
            Metazoa & 1491012 & 30758 & 22373
              & 1328135 & 0 & 0 & 930 & 25535 & 4423 & 1665 & 130324 \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{Kingdom (leaf nodes)}
        \label{table:Kingdom leaf nodes}
      \end{table}

      \begin{table}[h!]
        \begin{center}
          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
            \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
              & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
            \hline \hline
            none & 84456 & 45 & 529 
              & 15035 & 243 & 25910 & 0 & 8764 & 6183 & 0 & 28140 \\
            Fungi & 324105 & 577 & 2983
              & 39088 & 0 & 0 & 0 & 5858 & 0 & 0 & 274803 \\
            Chloroplastida & 460457 & 3519 & 77
              & 454211 & 0 & 0 & 0 & 4688 & 0 & 0 & 1558 \\
            Metazoa & 1670956 & 30758 & 22373
              & 1485749 & 0 & 0 & 1313 & 29002 & 5102 & 1957 & 147833 \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{Kingdom (inkl internal nodes)}
        \label{table:Kingdom internal nodes}
      \end{table}

@@

        Weinstein and Kuris have been searching for origins of parasitism in Animalia \cite{Weinstein2016}. 
          They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in Arthropoda $\supset$ 87 
          in Insecta. \\
        This has led us to count the origins and losses of parasitism in our investigation as well. \\
        We count only one origin / loss in a parent node with different children's nodes. \\
        Here we have encountered a problem: The Castor algorithm gives us probabilities for states. That 
          means there are also nodes with state like 0.3 or 0.5. So how do \colorbox{red}{you} count? Our solution was, 
          to round these values. We have to say that we round 0.5 to 0.

@@

        Lets have a look at the same phyla as in the section before: Chordata, Nematoda, 
          Platyhelminthes and Apicomplexa. \\
        Chordata are full of free-living species and so we see only a few origins of parasitism. The root
        and mostly all species are predicted as free-living. \\
        In Apicomplexa and the Platyhelminthes are looking fine too. Our algorithm gives us only one loss 
          of parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over 
          mostly all species predicted as parasites. \\
        Nematoda is again full of problems. The rootnode is predicted as a parasite and so we have more 
          losses of parasitism for the less information of free-living species in this phylum. The rest 
          is parasitic \\
          As we have already mentioned Blaxter et al. found at least seven origins of parasitism 
            \cite{Blaxter1998}. If we assume that the root node of Nematoda is free-living, then some 
            losses would have to turn around and become Origins. So it could be that we end up in a similar 
            size as Blaxter.

        \begin{lstlisting}[gobble=6]
          possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
          rounded to:    0  0      0    0    1      1     1
        \end{lstlisting}

        % \begin{lstlisting}[gobble=6]
        %   # possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
        %   # rounded to:    0  0      0    0    1      1     1
        %   if node_state != father_state:
        %     if father_state == 0:
        %         origins += 1        # FL -> P
        %         new_found = True
        %     else:
        %         losses += 1         # P -> FL
        %         new_found = True
        % \end{lstlisting}

        % \todo{without rounding change else: to elif $father_state == 1$}

>>>>

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Biological view} \label{sec:biological view}
      To analyze the results, we have selected some phyla (subtrees) to evaluate our results 
        selectively from the biological point of view: Chordata, Nematoda, Platyhelminthes and 
        Apicomplexa. \\
      In Table \ref{table:phylum leaf nodes states} we compare the given states with the predicted ones. \\
      Several factors such as the distribution of existing input data via parasitics and free-livings, 
        faulty input data from GloBI and reinforcement of errors by multifurcation play an important 
        role, which crystallize out in these examples. \\
      An important factor here is that the credibility of the results. The accuracy of the input data 
        stands and falls with the presence and the correctness of the data of GloBI. Errors of incorrect 
        input data can be amplified by incorrect prediction of unknown species and can be reversed in 
        order to improve the data situation of GloBI. \\
      Since we look at such large trees we can not expect to know all the parasites, so we look at 
        individual positives. This is positive in the sense that the majority have the opposite state.

      \begin{table}
        \begin{center}
          \begin{tabular}{ |l|r||r|r||r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{4}{c|}{\bfseries final states} \\
            \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P & \bfseries 0 \bfseries (FL) & \bfseries 0.3 &\bfseries  0.5 & \bfseries 1 (P) \\
            \hline \hline
            Chordata & 91785        & 10451 & 18          & 91759 & 0 & 0 & 26 \\
            &                       & 99.83~\% & 0.49~\%  & 99.97~\% & & & 0.03~\% \\ \hline
            Nematoda & 30127        & 21 & 3289           & 1604 & 142 & 1196 & 27185 \\
            &                       & 0.63~\% & 99.37~\%  & 5.32~\% & 0.47~\% & 3.97~\% & 90.23~\% \\ \hline
            Platyhelminthes & 22683 & 7 & 7086            & 175 & & & 22508 \\
            &                       & 0.1~\% & 99.9~\%    & 0.77~\% & 0 & 0 & 99.23~\% \\ \hline
            Apicomplexa & 1863      & 1 & 255             & 1 & 0 & 0 & 1862 \\
            &                       & 0.39~\% & 99.61~\%  & 0.05~\% & & & 99.95~\% \\
            % \hline \hline
            % Phylum & \# nodes & FL & P
            %   & 0 (FL) & 0.4 & 0.5 & 0.67 & 0.75 & 1 (P) \\
            % Arthropoda & 1198981 & 18912 & 11141 
            %   & 1099509 & 1313 & 22478 & 4176 & 1665 & 70223 \\
            % & & 62.93~\% & 37.07~\%
            %   & 91.7~\% & 0.11~\% & 1.87~\% & 0.35~\% & 0.14~\% & 5.86~\% \\
            \hline
          \end{tabular} 
        \end{center}
        \caption{Some selected phyla (subtrees), only leaf nodes, were examined for the evolution 
          of the amount and percentage of given data to predicted data.}
        \label{table:phylum leaf nodes states} 
      \end{table}

      In contrast to the other phyla examined, the phylogeny in the Chordata is more pronounced (less 
        multifurcation) (see Table \ref{table:percentage loss information subtrees}). This results in 
        less variance of errors. What is reflected in the results from the table 
        \ref{table:phylum leaf nodes states}. There are 18 parasites as input data and only 8 more are 
        predicted. The Chordata mostly consist of free-living species, so this seems believable. We 
        started with 99.83~\%  species and predict 99.97~\% species as free-living (including already 
        known nodes).

      \begin{figure}[h!]
        \centering
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
        \caption{Parasites of Phylum: Chordata. \\
          All parasite data of the chordata were mapped into a rough taxonomy (phylum, class, order, 
            family) in order to understand their distribution and affiliation. \\
          The internal nodes are the wanted taxa from OTL (with the addition of \# input parasites to 
            $\rightarrow$ \# predicted parasites). \\
          The leaf nodes are the input parasites (green) and the predicted parasites (white $\rightarrow$ 
            green).}
        \label{fig:ChordataParasites}
      \end{figure}

      We mapped the few parasitic species in a \colorbox{red}{rough/simple} taxonomy (see Figure \ref{fig:ChordataParasites}): \\
      Known parasitic birds belong to the order Sauria. Here we know from Rothschild  here there are 
        breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
        got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
        \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
        known as broodparasite and some others. \\
      An example of the amplification of mistakes here are the carp. There is a paper from which GloBI 
        concludes: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
        (\textit{Cyprinus carpio})\footnote{
          \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
          {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio}
        }. Since there is hardly any information about free-living, it follows that all siblings are 
        also predicted to be parasitic. \\
        % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
        % Snake: Storeria dekayi (probably caused by wrong input data.)
      % \begin{itemize}
      %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
      %   \item Order Anura (1): a toad (Family Bufonidae) - there exists some parasitic species in here, 
      %     they eat fin or pieces of larger fish.
      %   \item Order Siluriformes (1): a catfish (Family Loricariidae) - there exists some parasitic 
      %     species in here.
      % \end{itemize}

@@

      Most species of Platyhelminthes (flatworms) are parasites, although there are also free-living, 
        predatory feeding species. These are summarized in the Turbellaria, while the parasites are 
        divided into three other classes \cite{Ax1961}. This also corresponds to our observations. There 
        is one class (Rhabditophora) that contains all but one single exception of free-living species 
        of this phylum, which includes the Turbellaria. \\
      It should be noted, however, that this classification is outdated, as it has been proven that 
        the Turbellaria are not monophyletic. But we will not go into that here. \\
      For the Platyhelminthes we had more state information for the leaf nodes compared to the other 
        considered subtrees, see Table \ref{table:percentage loss information subtrees}. We start with 
        0.1~\% free-livings and predicted 0.77~\% as free-living species. \\

      With the Nematoda it looks more complicated. Large parts of Nematoda are free-living, but we 
        found only 5.32~\% of them. Blaxter et al. estimates the order of 25,000 parasites in the 
        Nematoda \cite{Blaxter2015} and speaks of at least seven independently arosed parasitism 
        \cite{Blaxter1998}. In a recent article Blaxter identifies 18 origins \cite{Blaxter2015} in 
        Nematoda. \\
      The problem at this point, however, is: Hallan speaks of the fact that only 23,000 species 
        were described by the Nematoda but is it assumed that one million or more species are in this 
        phylum.\footnote{J. Hallan, unpublished; 
          \hyperlink{https://insects.tamu.edu/research/collection/hallan/}
          {https://insects.tamu.edu/research/collection/hallan/}
        }. \todo{Link ist nicht erreichbar!} The parasites have been much more studied and thus we start 
        with only 0.63~\% (table \ref{table:phylum leaf nodes states}) free-living species. Against such 
        a shifted data situation, the algorithm is almost powerless to make correct predictions. And yet 
        the percentage has increased to 5.34~\%. \\

@@

      \begin{table}[h!]
        \begin{center}
          \begin{tabular}{ |l|r||r|r||r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{6}{c|}{\bfseries final states} \\
            \bfseries Phylum & \bfseries \# nodes & \bfseries FL & \bfseries P
              & \bfseries 0 (FL) & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
            \hline \hline
            Chordata & 122546 & 10451 & 18 
              & 122473 & 0 & 0 & 0 & 0 & 73 \\
            Nematoda & 33564 & 21 & 3289 
              & 846 & 0 & 1133 & 0 & 0 & 31585 \\
            Platyhelminthes & 27142 & 7 & 7086 
              & 1010 & 0 & 175 & 0 & 0 & 25957 \\
            Apicomplexa & 2102 & 1 & 255 
              & 1 & 0 & 0 & 0 & 0 & 2101 \\
            % \hline
            % Arthropoda & 1319460 & 18912 & 11141 
            %   & 1207204 & 1313 & 25499 & 4852 & 1957 & 78635 \\
            \hline
          \end{tabular}
        \end{center}
        \caption{Some selected phyla (subtrees), including internal nodes, were examined for the evolution 
        of the amount and percentage of given data to predicted data.}
        \label{table:Phylum internal nodes}
      \end{table}

      \begin{table}[h!]
        \begin{center}
          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
            \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
              & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
            \hline \hline
            none & 75446 & 45 & 529 
              & 13426 & 220 & 24082 & 0 & 7792 & 5302 & 0 & 24493 \\
            Fungi & 31457 & 577 & 2983
              & 38520 & 0 & 0 & 0 & 5723 & 0 & 0 & 266463 \\
            Chloroplastida & 416478 & 3519 & 77
              & 410795 & 0 & 0 & 0 & 4182 & 0 & 0 & 1501 \\
            Metazoa & 1491012 & 30758 & 22373
              & 1328135 & 0 & 0 & 930 & 25535 & 4423 & 1665 & 130324 \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{All kingdoms (subtrees), only leaf nodes, were examined for the evolution of the 
          amount and percentage of given data to predicted data.}
        \label{table:Kingdom leaf nodes}
      \end{table}

      \begin{table}[h!]
        \begin{center}
          \hspace*{-2cm}\begin{tabular}{ |l|r||r|r||r|r|r|r|r|r|r|r| }
            \hline
            & & \multicolumn{2}{c||}{\bfseries original states} & \multicolumn{8}{c|}{\bfseries final states} \\
            \bfseries Kingdom & \bfseries \# nodes & \bfseries FL & \bfseries P
              & \bfseries 0 (FL) & \bfseries 0.25 & \bfseries 0.33 & \bfseries 0.4 & \bfseries 0.5 & \bfseries 0.67 & \bfseries 0.75 & \bfseries 1 (P) \\
            \hline \hline
            none & 84456 & 45 & 529 
              & 15035 & 243 & 25910 & 0 & 8764 & 6183 & 0 & 28140 \\
            Fungi & 324105 & 577 & 2983
              & 39088 & 0 & 0 & 0 & 5858 & 0 & 0 & 274803 \\
            Chloroplastida & 460457 & 3519 & 77
              & 454211 & 0 & 0 & 0 & 4688 & 0 & 0 & 1558 \\
            Metazoa & 1670956 & 30758 & 22373
              & 1485749 & 0 & 0 & 1313 & 29002 & 5102 & 1957 & 147833 \\
            \hline  
          \end{tabular}
        \end{center}
        \caption{All kingdoms (subtrees), inkluding internal nodes, were examined for the evolution of the 
        amount and percentage of given data to predicted data.}
        \label{table:Kingdom internal nodes}
      \end{table}

@@

        Weinstein and Kuris have been searching for origins of parasitism in Animalia \cite{Weinstein2016}. 
          They identified 223 parasitic origins: 223 in Metazoa $\supset$ 143 in Arthropoda $\supset$ 87 
          in Insecta. \\
        This has led us to count the origins and losses of parasitism in our investigation as well. \\
        We count only one origin / loss in a parent node with different children's nodes. \\
        Here we have encountered a problem: The Castor algorithm gives us probabilities for states. That 
          means there are also nodes with state like 0.3 or 0.5. The question is, how to count these state 
          changes. We decided to round the values.
        % \begin{lstlisting}[gobble=6]
        %   possible tags: 0, 0.333, 0.4, 0.5, 0.667, 0.75, 1
        %   rounded to:    0  0      0    0    1      1     1
        % \end{lstlisting}

@@

        When more closely regarding the same phyla as in the section before: Chordata, Nematoda, 
          Platyhelminthes and Apicomplexa. \\
        Chordata are full of free-living species and so we see only a few origins of parasitism. The root
        and mostly all species are predicted as free-living. \\
        In Apicomplexa and the Platyhelminthes also look credible. Our algorithm gives us only one loss of
          parasitism in Apicomplexa and five in the Platyhelminthes. They are both from the root over
          mostly all species predicted as parasites. \\
        Nematoda is again full of problems. The rootnode is predicted as a parasite and so we have more 
          losses of parasitism for the less information of free-living species in this phylum. The rest 
          is parasitic \\
        As we have already mentioned Blaxter et al. found at least seven origins of parasitism 
          \cite{Blaxter1998}. If we assume that the root node of Nematoda is free-living, then some 
          losses would have to turn around and become Origins. So it could be that we end up in a similar 
          size as Blaxter.
